Static Analysis by Path Focusing

### 2011-05-18 report/report.tex
update of the report - Real experiments still need to be done

	In the case of path focusing algorithm, we simply conjunct our formula with
	$(i \neq j) \vee (x'_j \neq x_i)$, such that the SMT-solving only proposes
	paths that are not the identity.

@@

@@

>>>>

	In the case of path focusing algorithm, we simply conjunct our formula with
	$(i \neq j) \vee (x'_j \neq x_i)$, such that the SMT-solving only proposes
	paths that are not the identity. Actually, it never focuses on such paths
	during the acending sequence, but during narrowing iterations that occur 
	at the end of the algorithm.

	Ignoring these identity transitions makes the narrowing sequence recover
	more precision.
	Indeed, narrowing sequence updates the invariant $X$ with $\Phi(X)$, which
	is still an invariant, while precision is recovered, meaning that $\Phi(X)
	\subset X$. In the case of an expansive function, where $X \subseteq
	\Phi(X)$, we never have $\Phi(X) \subset X$, so narrowing iterations are
	useless.

@@

	\subsection{Benchmarks}

@@

	\subsection{Analysis of real code}

	In this section, we show that \emph{Path Focusing} technique performs better
	that \emph{Lookahead} widening on some code taken from real open-source
	programs.

	To Be Completed\dots
